Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-05-12 tex/ms.tex
fix definition covariance matrix in alternative formulation

XXX Alternative XXX
To avoid making the logarithmic transform described above, which
distorts the errors, we can formulate the problem in a different way,
modifying Equation \label{eq:spectroscopicLF} above as 
\begin{eqnarray}\label{eq:spectroscopicLF_v2}
\ln p(d\given\theta,\alpha) &=&
                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
                                + \ln([2\pi]^N\,\det{C}) \right]
\\
\Delta &\equiv& d - \mu(\theta) * f(\alpha) 
\\
C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} * \mu)^2]\,\delta_{nn'} +
\transpose{\mu} \, K_\alpha(\lambda_n - \lambda_{n'}) \, \mu
\quad ,
\end{eqnarray}
where the multiplication of $s$ and $K_\alpha$ by $\mu$ in the
construction of $C_{nn'}$ means that they are defined in
\emph{fractional} terms, and the uncertainties remain Gaussian in
linear flux space.  It remains to be seen whether this actually works.

>>>>

XXX Alternative XXX
To avoid making the logarithmic transform described above, which
distorts the errors, we can formulate the problem in a different way,
modifying Equation \label{eq:spectroscopicLF} above as 
\begin{eqnarray}\label{eq:spectroscopicLF_v2}
\ln p(d\given\theta,\alpha) &=&
                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
                                + \ln([2\pi]^N\,\det{C}) \right]
\\
\Delta &\equiv& d - \mu(\theta) * f(\alpha) 
\\
C_{nn'} &\equiv& [\sigma_n^2 + (\hat{s} * \mu)^2]\,\delta_{nn'} +
 K_\alpha(\lambda_n - \lambda_{n'}) \ast \mu \, \transpose{\mu}
\quad ,
\end{eqnarray}
where $\ast$ denotes element-wise multiplication and the
multiplication of $s$ and $K_\alpha$ by $\mu$ and
$\mu\,\transpose{\mu}$ respectively in the construction of $C_{nn'}$
means that they are defined in \emph{fractional} terms, and the
uncertainties remain Gaussian in linear flux space.  It remains to be
seen whether this actually works.
